---
title: "Linearity-EOS Transects"
author: "Meg Raisle"
date: "10/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(ggplot2)
library(tidyr)
library(dplyr)
library(wesanderson)
library('knitr')
```

## Linearity-EOS Transects 

```{r readData, echo=FALSE}
#import all data we want here

allecuavg <- read.csv(here("Picarro/EOSTransects/allecuavg.csv"))
comboecuavg <- read.csv(here("Picarro/EOSTransects/comboecuavg.csv"))
july15test <- read.csv(here("Picarro/EOSTransects/july15test.csv"))

allecuavg <- allecuavg %>%
  select(Day, Sample, Avg_iCO2, StdDev_iCO2)
```

### All Ecuador Samples Run During EOS Transects 
```{r data, eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 20}
kable(allecuavg, format = "markdown")

```
You can see above that there is a lot of variability between ecuador samples and the standard deviations vary pretty signficantly. Wondering if we should have a conversation about narrowing the window which I'm callign the gas pull . . . would be alot of work and not sure if it is the right thing to do, but worth a discussion.

### Results of Delta_iCO2 Differences from July 15 Linearity Test 
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 20}
kable(july15test, format = "markdown")

```

## Average, Standard Deviation, and Correction of All EOS Ecuador Bags
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 20}
kable(comboecuavg, format = "markdown")

```
I haven't yet run variance because it would not let me run with such a small sample size and thought we might have a discussion about this data before proceeding