---
title: "Flux at Collar Transects"
author: "Chloe"
date: "Data from 7/16/2019 measurements"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("here")
install.packages("ggplot2")
install.packages("tidyr")
install.packages("dplyr")
install.packages("wesanderson")
install.packages("knitr")
install.packages("ggpubr")
# Plots and Analysis
library(here)
library(ggplot2)
library(tidyr)
library(dplyr)
library(wesanderson)
library('knitr')
library(ggpubr)

```

## Plots and Analysis

```{r , echo=FALSE}
#flux of synoptics 

date<- "07182019"


# eos1 data
eos2 <- read.csv(here("FieldData/EosFD",paste0("eos2_",date,".csv")))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm.,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos2) <- c("DateTime","Flux_eos2","Temp_C_eos2","CO2_Soil_ppm_eos2","CO2_Soil_STD_ppm_eos2",
                    "CO2_ATM_ppm_eos2","CO2_ATM_STD_ppm_eos2","Mode")


# Subset data so only records at 5 minute intervals are retained
sub.1 <- subset(eos2, format(DateTime,'%OS')=='00')
sub.2 <- subset(sub.1, format(DateTime,'%M')%in% c("00","05","10","15","20","25","30","35","40","45","50","55","60"))

row.names(sub.2) <- NULL

col1.1 <- sub.2[434:439,]
col2.1 <- sub.2[442:446,]
col3.1 <- sub.2[451:455,]
col4.1 <- sub.2[460:464,]
col5.1 <- sub.2[471:475,]
col6.1 <- sub.2[479:484,]
col7.1 <- sub.2[487:493,]

```


Flux of Collars 7-16-2019

col1.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.1 <- select(col1.1,DateTime, Flux_eos2)
kable(head(col1.1), format = "markdown", row.names = FALSE)

```

col2.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.1 <- select(col2.1,DateTime, Flux_eos2)
kable(head(col2.1), format = "markdown", row.names = FALSE)

```
col3.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.1 <- select(col3.1,DateTime, Flux_eos2)
kable(head(col3.1), format = "markdown", row.names = FALSE)

```
col4.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.1 <- select(col4.1,DateTime, Flux_eos2)
kable(head(col4.1), format = "markdown", row.names = FALSE)

```
col5.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.1 <- select(col5.1,DateTime, Flux_eos2)
kable(head(col5.1), format = "markdown", row.names = FALSE)

```
col6.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.1 <- select(col6.1,DateTime, Flux_eos2)
kable(head(col6.1), format = "markdown", row.names = FALSE)

```
col7.1
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.1 <- select(col7.1,DateTime, Flux_eos2)
kable(head(col7.1), format = "markdown", row.names = FALSE)

```

Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.1avg <- mean(col1.1$Flux_eos2)
col2.1avg <- mean(col2.1$Flux_eos2)
col3.1avg <- mean(col3.1$Flux_eos2)
col4.1avg <- mean(col4.1$Flux_eos2)
col5.1avg <- mean(col5.1$Flux_eos2)
col6.1avg <- mean(col6.1$Flux_eos2)
col7.1avg <- mean(col7.1$Flux_eos2)

col1.1sd <- sd(col1.1$Flux_eos2)
col2.1sd <- sd(col2.1$Flux_eos2)
col3.1sd <- sd(col3.1$Flux_eos2)
col4.1sd <- sd(col4.1$Flux_eos2)
col5.1sd <- sd(col5.1$Flux_eos2)
col6.1sd <- sd(col6.1$Flux_eos2)
col7.1sd <- sd(col7.1$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.1avg,col2.1avg,col3.1avg,col4.1avg,col5.1avg,col6.1avg,col7.1avg))
rownames(a) <- c("col1.1", "col2.1", "col3.1", "col4.1", "col5.1", "col6.1", "col7.1")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.1sd,col2.1sd,col3.1sd,col4.1sd,col5.1sd,col6.1sd,col7.1sd))
rownames(sd) <- c("col1.1", "col2.1", "col3.1", "col4.1", "col5.1", "col6.1", "col7.1")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

 
```

collars 7-16-2019
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
avgplot1 <- ggplot(a)+
 geom_errorbar(aes(x= 1:7,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:7, y= AverageFlux), color = "blue", size = 2)

avgplot1 <- avgplot1 + scale_x_continuous(breaks=1:7, labels=c("col1.1", "col2.1", "col3.1", "col4.1", "col5.1", "col6.1", "col7.1")) +
labs(x = "7-16-2019 Collar", y = "Average FLux")
        

avgplot1

```

```{r , echo=FALSE}
#flux of synoptics 

date<- "07222019"


# eos1 data
eos2 <- read.csv(here("FieldData/EosFD",paste0("eos2_",date,".csv")))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm..,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos2) <- c("DateTime","Flux_eos2","Temp_C_eos2","CO2_Soil_ppm_eos2","CO2_Soil_STD_ppm_eos2",
                    "CO2_ATM_ppm_eos2","CO2_ATM_STD_ppm_eos2","Mode")


# Subset data so only records at 5 minute intervals are retained
sub.1 <- subset(eos2, format(DateTime,'%OS')=='00')
sub.2 <- subset(sub.1, format(DateTime,'%M')%in% c("00","05","10","15","20","25","30","35","40","45","50","55","60"))

rownames(sub.2) <- NULL
sub.2$Flux_eos2 <- as.numeric(as.character(sub.2$Flux_eos2))

col1.2 <- sub.2[1758:1761,]
col2.2 <- sub.2[1754:1757,]
col3.2 <- sub.2[1748:1752,]
col4.2 <- sub.2[1743:1746,]
col5.2 <- sub.2[1711:1714,]
col6.2 <- sub.2[1716:1719,]
col7.2 <- sub.2[1726:1729,]
col8.2 <- sub.2[1732:1735,]
```


Flux of Collars 7-22-2019

col1.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.2 <- select(col1.2,DateTime, Flux_eos2)
kable(head(col1.2), format = "markdown", row.names = FALSE)

```

col2.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.2 <- select(col2.2,DateTime, Flux_eos2)
kable(head(col2.2), format = "markdown", row.names = FALSE)

```
col3.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.2 <- select(col3.2,DateTime, Flux_eos2)
kable(head(col3.2), format = "markdown", row.names = FALSE)

```
col4.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.2 <- select(col4.2,DateTime, Flux_eos2)
kable(head(col4.2), format = "markdown", row.names = FALSE)

```
col5.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.2 <- select(col5.2,DateTime, Flux_eos2)
kable(head(col5.2), format = "markdown", row.names = FALSE)

```
col6.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.2 <- select(col6.2,DateTime, Flux_eos2)
kable(head(col6.2), format = "markdown", row.names = FALSE)

```
col7.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.2 <- select(col7.2,DateTime, Flux_eos2)
kable(head(col7.2), format = "markdown", row.names = FALSE)

```
col8.2
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.2 <- select(col8.2,DateTime, Flux_eos2)
kable(head(col8.2), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site 
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.2avg <- mean(col1.2$Flux_eos2)
col2.2avg <- mean(col2.2$Flux_eos2)
col3.2avg <- mean(col3.2$Flux_eos2)
col4.2avg <- mean(col4.2$Flux_eos2)
col5.2avg <- mean(col5.2$Flux_eos2)
col6.2avg <- mean(col6.2$Flux_eos2)
col7.2avg <- mean(col7.2$Flux_eos2)
col8.2avg <- mean(col8.2$Flux_eos2)

col1.2sd <- sd(col1.2$Flux_eos2)
col2.2sd <- sd(col2.2$Flux_eos2)
col3.2sd <- sd(col3.2$Flux_eos2)
col4.2sd <- sd(col4.2$Flux_eos2)
col5.2sd <- sd(col5.2$Flux_eos2)
col6.2sd <- sd(col6.2$Flux_eos2)
col7.2sd <- sd(col7.2$Flux_eos2)
col8.2sd <- sd(col8.2$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.2avg,col2.2avg,col3.2avg,col4.2avg,col5.2avg,col6.2avg,col7.2avg,col8.2avg ))
rownames(a) <- c("col1.2", "col2.2", "col3.2", "col4.2", "col5.2", "col6.2", "col7.2","col8.2")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.2sd,col2.2sd,col3.2sd,col4.2sd,col5.2sd,col6.2sd,col7.2sd,col8.2sd))
rownames(sd) <- c("col1.2", "col2.2", "col3.2", "col4.2", "col5.2", "col6.2", "col7.2", "col8.2")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

avgplot2 <- ggplot(a)+
 geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "blue", size = 2)
avgplot2 <- avgplot2 + scale_x_continuous(breaks=1:8, labels=c("col1", "col2", "col3", "col4", "col5", "col6", "col7","col8")) +
labs(x = "7-22-2019 Collar", y = "Average FLux")
        

avgplot2

allplotz <- avgplot1 +  geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="green") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "green", size = 2)

```


```{r , echo=FALSE}
#flux of synoptics 

date<- "07312019"


# eos1 data
eos2 <- read.csv(here("FieldData/EosFD",paste0("eos2_",date,".csv")))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm..,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos2) <- c("DateTime","Flux_eos2","Temp_C_eos2","CO2_Soil_ppm_eos2","CO2_Soil_STD_ppm_eos2",
                    "CO2_ATM_ppm_eos2","CO2_ATM_STD_ppm_eos2","Mode")

eos1 <- read.csv(here("FieldData/EosFD/eos1_FIX_07312019.csv"))
eos1 <- eos1%>%
  select(DateTime,Flux_1,Temp_C_1,CO2_Soil_1,
        CO2_Soil_STD_1,CO2_ATM_1,CO2_ATM_STD_1,Mode_1)
colnames(eos1) <- c("DateTime","Flux_eos1","Temp_C_eos1","CO2_Soil_ppm_eos1","CO2_Soil_STD_ppm_eos1","CO2_ATM_ppm_eos1","CO2_ATM_STD_ppm_eos1","Mode")

eos1$Flux_eos1 <- as.numeric(as.character(eos1$Flux_eos1))

col1.3 <- eos1[2321:2324,]
col2.3 <- eos1[2326:2329,]
col3.3 <- eos1[2331:2334,]
col4.3 <- eos1[2336:2339,]
col5.3 <- eos2[1613:1617,]
col6.3 <- eos2[1619:1623,]
col7.3 <- eos2[1625:1628,]
col8.3 <- eos2[1631:1634,]

```


Flux of Collars 7-29-2019

col1.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.3 <- select(col1.3,DateTime, Flux_eos1)
kable(head(col1.3), format = "markdown", row.names = FALSE)

```

col2.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.3 <- select(col2.3,DateTime, Flux_eos1)
kable(head(col2.3), format = "markdown", row.names = FALSE)

```
col3.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.3 <- select(col3.3,DateTime, Flux_eos1)
kable(head(col3.3), format = "markdown", row.names = FALSE)

```
col4.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.3 <- select(col4.3,DateTime, Flux_eos1)
kable(head(col4.3), format = "markdown", row.names = FALSE)

```
col5.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.3 <- select(col5.3,DateTime, Flux_eos2)
kable(head(col5.3), format = "markdown", row.names = FALSE)

```
col6.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.3 <- select(col6.3,DateTime, Flux_eos2)
kable(head(col6.3), format = "markdown", row.names = FALSE)

```
col7.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.3 <- select(col7.3,DateTime, Flux_eos2)
kable(head(col7.3), format = "markdown", row.names = FALSE)

```
col8.3
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.3 <- select(col8.3,DateTime, Flux_eos2)
kable(head(col8.3), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.3avg <- mean(col1.3$Flux_eos1)
col2.3avg <- mean(col2.3$Flux_eos1)
col3.3avg <- mean(col3.3$Flux_eos1)
col4.3avg <- mean(col4.3$Flux_eos1)
col5.3avg <- mean(col5.3$Flux_eos2)
col6.3avg <- mean(col6.3$Flux_eos2)
col7.3avg <- mean(col7.3$Flux_eos2)
col8.3avg <- mean(col8.3$Flux_eos2)

col1.3sd <- sd(col1.3$Flux_eos1)
col2.3sd <- sd(col2.3$Flux_eos1)
col3.3sd <- sd(col3.3$Flux_eos1)
col4.3sd <- sd(col4.3$Flux_eos1)
col5.3sd <- sd(col5.3$Flux_eos2)
col6.3sd <- sd(col6.3$Flux_eos2)
col7.3sd <- sd(col7.3$Flux_eos2)
col8.3sd <- sd(col8.3$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.3avg,col2.3avg,col3.3avg,col4.3avg,col5.3avg,col6.3avg,col7.3avg, col8.3avg))
rownames(a) <- c("col1.3", "col2.3", "col3.3", "col4.3", "col5.3", "col6.3", "col7.3", "col8.3")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.3sd,col2.3sd,col3.3sd,col4.3sd,col5.3sd,col6.3sd,col7.3sd, col8.3sd))
rownames(sd) <- c("col1.3", "col2.3", "col3.3", "col4.3", "col5.3", "col6.3", "col7.3", "col8.3")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)
 
avgplot3 <- ggplot(a)+
 geom_errorbar(aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:8, y= AverageFlux), color = "blue", size = 2)

avgplot3 <- avgplot3 + scale_x_continuous(breaks=1:8, labels=c("col1", "col2", "col3", "col4", "col5", "col6", "col7", "col8")) +
labs(x = "7-29-2019 Collar", y = "Average FLux")
avgplot3

allplotz <- allplotz +  geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="red") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "red", size = 2)
```

```{r , echo=FALSE}
#flux of synoptics 

date<- "08012019"


# eos2 data
eos2 <- read.csv(here("FieldData/EosFD",paste0("eos2_",date,".csv")))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm..,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos2) <- c("DateTime","Flux_eos2","Temp_C_eos2","CO2_Soil_ppm_eos2","CO2_Soil_STD_ppm_eos2",
                    "CO2_ATM_ppm_eos2","CO2_ATM_STD_ppm_eos2","Mode")


col1.4 <- eos2[2536:2539,]
col2.4 <- eos2[2532:2535,]
col3.4 <- eos2[2515:2517,]
col4.4 <- eos2[2544:2547,]
col5.4 <- eos2[2507:2510,]
col6.4 <- eos2[2511:2514,]
col7.4 <- eos2[2515:2517,]
col8.4 <- eos2[2520:2523,]

```


### Flux of Collars 

col1.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.4 <- select(col1.4,DateTime, Flux_eos2)
kable(head(col1.4), format = "markdown", row.names = FALSE)

```

col2.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.4 <- select(col2.4,DateTime, Flux_eos2)
kable(head(col2.4), format = "markdown", row.names = FALSE)

```
col3.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.4 <- select(col3.4,DateTime, Flux_eos2)
kable(head(col3.4), format = "markdown", row.names = FALSE)

```
col4.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.4 <- select(col4.4,DateTime, Flux_eos2)
kable(head(col4.4), format = "markdown", row.names = FALSE)

```
col5.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.4 <- select(col5.4,DateTime, Flux_eos2)
kable(head(col5.4), format = "markdown", row.names = FALSE)

```
col6.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.4 <- select(col6.4,DateTime, Flux_eos2)
kable(head(col6.4), format = "markdown", row.names = FALSE)

```
col7.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.4 <- select(col7.4,DateTime, Flux_eos2)
kable(head(col7.4), format = "markdown", row.names = FALSE)

```
col8.4
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.4 <- select(col8.4,DateTime, Flux_eos2)
kable(head(col8.4), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.4avg <- mean(col1.4$Flux_eos2)
col2.4avg <- mean(col2.4$Flux_eos2)
col3.4avg <- mean(col3.4$Flux_eos2)
col4.4avg <- mean(col4.4$Flux_eos2)
col5.4avg <- mean(col5.4$Flux_eos2)
col6.4avg <- mean(col6.4$Flux_eos2)
col7.4avg <- mean(col7.4$Flux_eos2)
col8.4avg <- mean(col8.4$Flux_eos2)

col1.4sd <- sd(col1.4$Flux_eos2)
col2.4sd <- sd(col2.4$Flux_eos2)
col3.4sd <- sd(col3.4$Flux_eos2)
col4.4sd <- sd(col4.4$Flux_eos2)
col5.4sd <- sd(col5.4$Flux_eos2)
col6.4sd <- sd(col6.4$Flux_eos2)
col7.4sd <- sd(col7.4$Flux_eos2)
col8.4sd <- sd(col8.4$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.4avg,col2.4avg,col3.4avg,col4.4avg,col5.4avg,col6.4avg,col7.4avg, col8.4avg))
rownames(a) <- c("col1.4", "col2.4", "col3.4", "col4.4", "col5.4", "col6.4", "col7.4", "col8.4")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.4sd,col2.4sd,col3.4sd,col4.4sd,col5.4sd,col6.4sd,col7.4sd, col8.4sd))
rownames(sd) <- c("col1.4", "col2.4", "col3.4", "col4.4", "col5.4", "col6.4", "col7.4", "col8.4")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

 
avgplot4 <- ggplot(a)+
 geom_errorbar(aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:8, y= AverageFlux), color = "blue", size = 2)

avgplot4 <- avgplot4 + scale_x_continuous(breaks=1:8, labels=c("col1", "col2", "col3", "col4", "col5", "col6", "col7", "col8")) +
labs(x = "8-01-2019 Collar", y = "Average FLux")
avgplot4

allplotz <- allplotz + geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="purple") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "purple", size = 2)
```

```{r , echo=FALSE}
#flux of synoptics 



# eos2 data
eos2 <- read.csv(here("FieldData/EosFD/eos2_08142019.csv"))

eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux)
colnames(eos2) <- c("DateTime","Flux_eos2")

eos2$Flux_eos2 <- as.numeric(as.character(eos2$Flux_eos2))

col1.5 <- eos2[2815:2818,]
col2.5 <- eos2[2820:2823,]
col3.5 <- eos2[2824:2826,]
col4.5 <- eos2[2829:2831,]
col5.5 <- eos2[2808:2811,]
col6.5 <- eos2[2796:2799,]
col7.5 <- eos2[2800:2803,]
col8.5 <- eos2[2804:2807,]

```


Flux of Collars 8-05-2019

col1.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.5 <- select(col1.5,DateTime, Flux_eos2)
kable(head(col1.5), format = "markdown", row.names = FALSE)

```

col2.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.5 <- select(col2.5,DateTime, Flux_eos2)
kable(head(col2.5), format = "markdown", row.names = FALSE)

```
col3.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.5 <- select(col3.5,DateTime, Flux_eos2)
kable(head(col3.5), format = "markdown", row.names = FALSE)

```
col4.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.5 <- select(col4.5,DateTime, Flux_eos2)
kable(head(col4.5), format = "markdown", row.names = FALSE)

```
col5.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.5 <- select(col5.5,DateTime, Flux_eos2)
kable(head(col5.5), format = "markdown", row.names = FALSE)

```
col6.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.5 <- select(col6.5,DateTime, Flux_eos2)
kable(head(col6.5), format = "markdown", row.names = FALSE)

```
col7.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.5 <- select(col7.5,DateTime, Flux_eos2)
kable(head(col7.5), format = "markdown", row.names = FALSE)

```
col8.5
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.5 <- select(col8.5,DateTime, Flux_eos2)
kable(head(col8.5), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.5avg <- mean(col1.5$Flux_eos2)
col2.5avg <- mean(col2.5$Flux_eos2)
col3.5avg <- mean(col3.5$Flux_eos2)
col4.5avg <- mean(col4.5$Flux_eos2)
col5.5avg <- mean(col5.5$Flux_eos2)
col6.5avg <- mean(col6.5$Flux_eos2)
col7.5avg <- mean(col7.5$Flux_eos2)
col8.5avg <- mean(col8.5$Flux_eos2)

col1.5sd <- sd(col1.5$Flux_eos2)
col2.5sd <- sd(col2.5$Flux_eos2)
col3.5sd <- sd(col3.5$Flux_eos2)
col4.5sd <- sd(col4.5$Flux_eos2)
col5.5sd <- sd(col5.5$Flux_eos2)
col6.5sd <- sd(col6.5$Flux_eos2)
col7.5sd <- sd(col7.5$Flux_eos2)
col8.5sd <- sd(col8.5$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.5avg,col2.5avg,col3.5avg,col4.5avg,col5.5avg,col6.5avg,col7.5avg, col8.5avg))
rownames(a) <- c("col1.5", "col2.5", "col3.5", "col4.5", "col5.5", "col6.5", "col7.5", "col8.5")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.5sd,col2.5sd,col3.5sd,col4.5sd,col5.5sd,col6.5sd,col7.5sd, col8.5sd))
rownames(sd) <- c("col1.5", "col2.5", "col3.5", "col4.5", "col5.5", "col6.5", "col7.5", "col8.5")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

 
avgplot5 <- ggplot(a)+
 geom_errorbar(aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:8, y= AverageFlux), color = "blue", size = 3)

avgplot5 <- avgplot5 + scale_x_continuous(breaks=1:8, labels=c("col1.5", "col2.5", "col3.5", "col4.5", "col5.5", "col6.5", "col7.5", "col8.5")) +
labs(x = "8-05-2019 Collar", y = "Average FLux")
avgplot5

allplotz<- allplotz + geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="yellow") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "yellow", size = 2)
```

```{r , echo=FALSE}
#flux of synoptics 

# eos2 data
eos2 <- read.csv(here("FieldData/EosFD/eos2_08142019.csv"))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux)
colnames(eos2) <- c("DateTime","Flux_eos2")

eos2$Flux_eos2 <- as.numeric(as.character(eos2$Flux_eos2))

col1.6 <- eos2[3280:3282,]
col2.6 <- eos2[3284:3286,]
col3.6 <- eos2[3288:3291,]
col4.6 <- eos2[3292:3295,]
col5.6 <- eos2[3262:3265,]
col6.6 <- eos2[3266:3269,]
col7.6 <- eos2[3270:3273,]
col8.6 <- eos2[3274:3277,]

```


Flux of Collars 8-08-2019

col1.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.6 <- select(col1.6,DateTime, Flux_eos2)
kable(head(col1.6), format = "markdown", row.names = FALSE)

```

col2.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.6 <- select(col2.6,DateTime, Flux_eos2)
kable(head(col2.6), format = "markdown", row.names = FALSE)

```
col3.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.6 <- select(col3.6,DateTime, Flux_eos2)
kable(head(col3.6), format = "markdown", row.names = FALSE)

```
col4.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.6 <- select(col4.6,DateTime, Flux_eos2)
kable(head(col4.6), format = "markdown", row.names = FALSE)

```
col5.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.6 <- select(col5.6,DateTime, Flux_eos2)
kable(head(col5.6), format = "markdown", row.names = FALSE)

```
col6.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.6 <- select(col6.6,DateTime, Flux_eos2)
kable(head(col6.6), format = "markdown", row.names = FALSE)

```
col7.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.6 <- select(col7.6,DateTime, Flux_eos2)
kable(head(col7.6), format = "markdown", row.names = FALSE)

```
col8.6
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.6 <- select(col8.6,DateTime, Flux_eos2)
kable(head(col8.6), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.6avg <- mean(col1.6$Flux_eos2)
col2.6avg <- mean(col2.6$Flux_eos2)
col3.6avg <- mean(col3.6$Flux_eos2)
col4.6avg <- mean(col4.6$Flux_eos2)
col5.6avg <- mean(col5.6$Flux_eos2)
col6.6avg <- mean(col6.6$Flux_eos2)
col7.6avg <- mean(col7.6$Flux_eos2)
col8.6avg <- mean(col8.6$Flux_eos2)

col1.6sd <- sd(col1.6$Flux_eos2)
col2.6sd <- sd(col2.6$Flux_eos2)
col3.6sd <- sd(col3.6$Flux_eos2)
col4.6sd <- sd(col4.6$Flux_eos2)
col5.6sd <- sd(col5.6$Flux_eos2)
col6.6sd <- sd(col6.6$Flux_eos2)
col7.6sd <- sd(col7.6$Flux_eos2)
col8.6sd <- sd(col8.6$Flux_eos2)

a <- data.frame(AverageFlux = c(col1.6avg,col2.6avg,col3.6avg,col4.6avg,col5.6avg,col6.6avg,col7.6avg, col8.6avg))
rownames(a) <- c("col1.6", "col2.6", "col3.6", "col4.6", "col5.6", "col6.6", "col7.6", "col8.6")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.6sd,col2.6sd,col3.6sd,col4.6sd,col5.6sd,col6.6sd,col7.6sd, col8.6sd))
rownames(sd) <- c("col1.6", "col2.6", "col3.6", "col4.6", "col5.6", "col6.6", "col7.6", "col8.6")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

 
avgplot6 <- ggplot(a)+
 geom_errorbar(aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:8, y= AverageFlux), color = "blue", size = 3)

avgplot6 <- avgplot6 + scale_x_continuous(breaks=1:8, labels=c("col1.6", "col2.6", "col3.6", "col4.6", "col5.6", "col6.6", "col7.6", "col8.6")) +
labs(x = "8-08-2019 Collar", y = "Average FLux")
avgplot6

allplotz <- allplotz + geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="orange") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "orange", size = 2)
```



```{r , echo=FALSE}
#flux of synoptic
eos1 <- read.csv(here("FieldData/EosFD/eos1_08132019.1.csv"))
eos1$Year <- paste0("20",eos1$Year)
eos1$dateTime <- as.POSIXct(as.character(paste0(eos1$Year,"-",eos1$Month,"-",eos1$Day," ",eos1$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos1 <- eos1%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm.,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos1) <- c("DateTime","Flux_eos1","Temp_C_eos1","CO2_Soil_ppm_eos1","CO2_Soil_STD_ppm_eos1",
                    "CO2_ATM_ppm_eos1","CO2_ATM_STD_ppm_eos1","Mode")
eos1$Flux_eos1 <- as.numeric(as.character(eos1$Flux_eos1))

eos2 <- read.csv(here("FieldData/EosFD/eos2_08142019.csv"))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux)
colnames(eos2) <- c("DateTime","Flux_eos2")

eos2$Flux_eos2 <- as.numeric(as.character(eos2$Flux_eos2))

col1.7 <- eos2[3701:3704,]
col2.7 <- eos2[3706:3709,]
col3.7 <- eos2[3711:3714,]
col4.7 <- eos2[3715:3718,]
col5.7 <- eos1[1344:1347,]
col6.7 <- eos1[1348:1351,]
col7.7 <- eos1[1352:1355,]
col8.7 <- eos1[1356:1359,]



```


Flux of Collars 9-13-2019

col1.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col1.7 <- select(col1.7,DateTime, Flux_eos2)
kable(head(col1.7), format = "markdown", row.names = FALSE)

```

col2.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col2.7 <- select(col2.7,DateTime, Flux_eos2)
kable(head(col2.7), format = "markdown", row.names = FALSE)

```
col3.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col3.7 <- select(col3.7,DateTime, Flux_eos2)
kable(head(col3.7), format = "markdown", row.names = FALSE)

```
col4.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col4.7 <- select(col4.7,DateTime, Flux_eos2)
kable(head(col4.7), format = "markdown", row.names = FALSE)

```
col5.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col5.7 <- select(col5.7,DateTime, Flux_eos1)
kable(head(col5.7), format = "markdown", row.names = FALSE)

```
col6.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col6.7 <- select(col6.7,DateTime, Flux_eos1)
kable(head(col6.7), format = "markdown", row.names = FALSE)

```
col7.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col7.7 <- select(col7.7,DateTime, Flux_eos1)
kable(head(col7.7), format = "markdown", row.names = FALSE)

```
col8.7
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

col8.7 <- select(col8.7,DateTime, Flux_eos1)
kable(head(col8.7), format = "markdown", row.names = FALSE)

```
Average Flux of Each Site
```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1.7avg <- mean(col1.7$Flux_eos2)
col2.7avg <- mean(col2.7$Flux_eos2)
col3.7avg <- mean(col3.7$Flux_eos2)
col4.7avg <- mean(col4.7$Flux_eos2)
col5.7avg <- mean(col5.7$Flux_eos1)
col6.7avg <- mean(col6.7$Flux_eos1)
col7.7avg <- mean(col7.7$Flux_eos1)
col8.7avg <- mean(col8.7$Flux_eos1)

col1.7sd <- sd(col1.7$Flux_eos2)
col2.7sd <- sd(col2.7$Flux_eos2)
col3.7sd <- sd(col3.7$Flux_eos2)
col4.7sd <- sd(col4.7$Flux_eos2)
col5.7sd <- sd(col5.7$Flux_eos1)
col6.7sd <- sd(col6.7$Flux_eos1)
col7.7sd <- sd(col7.7$Flux_eos1)
col8.7sd <- sd(col8.7$Flux_eos1)

a <- data.frame(AverageFlux = c(col1.7avg,col2.7avg,col3.7avg,col4.7avg,col5.7avg,col6.7avg,col7.7avg, col8.7avg))
rownames(a) <- c("col1.7", "col2.7", "col3.7", "col4.7", "col5.7", "col6.7", "col7.7", "col8.7")
kable(a, format = "markdown", row.names = TRUE)

sd <- data.frame(StdDev=
c(col1.7sd,col2.7sd,col3.7sd,col4.7sd,col5.7sd,col6.7sd,col7.7sd, col8.7sd))
rownames(sd) <- c("col1.7", "col2.7", "col3.7", "col4.7", "col5.7", "col6.7", "col7.7", "col8.7")
kable(sd, format = "markdown", row.names = TRUE)

a <- cbind(a,sd)

 
avgplot7 <- ggplot(a)+
 geom_errorbar(aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="blue") +
  geom_point(aes(x= 1:8, y= AverageFlux), color = "blue", size = 3)

avgplot7 <- avgplot7 + scale_x_continuous(breaks=1:8, labels=c("col1.7", "col2.7", "col3.7", "col4.7", "col5.7", "col6.7", "col7.7", "col8.7")) +
labs(x = "8-13-2019 Collar", y = "Average FLux")
avgplot7

allplotz <- allplotz + geom_errorbar(data = a, aes(x= 1:8,ymin= AverageFlux - StdDev, ymax= AverageFlux + StdDev), width=0.2, size=1, color="brown") +
  geom_point(data = a, aes(x= 1:8, y= AverageFlux), color = "brown", size = 2)
```

All transect days


```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
allplot <- ggarrange(avgplot1, avgplot2, avgplot3, avgplot4, avgplot5, avgplot6, avgplot7)
allplot
allplotz


```

Average and standard deviation of each transect day at each collar 

```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

c1a <- t(data.frame(col1.1avg, col1.2avg, col1.3avg, col1.4avg, col1.5avg, col1.6avg, col1.7avg))
c2a <- t(data.frame(col2.1avg, col2.2avg, col2.3avg, col2.4avg, col2.5avg, col2.6avg, col2.7avg))
c3a <- t(data.frame(col3.1avg, col3.2avg, col3.3avg, col3.4avg, col3.5avg, col3.6avg, col3.7avg))
c4a<- t(data.frame(col4.1avg, col4.2avg, col4.3avg, col4.4avg, col4.5avg, col4.6avg, col4.7avg))
c5a<- t(data.frame(col5.1avg, col5.2avg, col5.3avg, col5.4avg, col5.5avg, col5.6avg, col5.7avg))
c6a<- t(data.frame(col6.1avg, col6.2avg, col6.3avg, col6.4avg, col6.5avg, col6.6avg, col6.7avg))
c7a<- t(data.frame(col7.1avg, col7.2avg, col7.3avg, col7.4avg, col7.5avg, col7.6avg, col7.7avg))
c8a<- t(data.frame(col8.2avg, col8.2avg, col8.3avg, col8.4avg, col8.5avg, col8.6avg, col8.7avg))

callavgs <- data.frame(cbind(c1a, c2a, c3a, c4a, c5a, c6a, c7a, c8a))
row.names(callavgs) <- c("Jul16", "Jul22", "Jul29", "Aug1", "Aug5", "Aug8", "Aug13")
colnames(callavgs) <- c("col1", "col2", "col3", "col4", "col5", "col6", "col7","col8")
kable(head(callavgs), format = "markdown", row.names = FALSE)

allavg <- data.frame(c(mean(callavgs$col1), mean(callavgs$col2), mean(callavgs$col3), mean(callavgs$col4), mean(callavgs$col5), mean(callavgs$col6), mean(callavgs$col7), mean(callavgs$col8)))
colnames(allavg) <- c("avgflux")
allsd <- data.frame(c(sd(callavgs$col1), sd(callavgs$col2), sd(callavgs$col3), sd(callavgs$col4), sd(callavgs$col5), sd(callavgs$col6), sd(callavgs$col7), sd(callavgs$col8)))
colnames(allsd) <- c("stddev")
allz <- cbind(allavg, allsd)

alltrans <- ggplot(allz) +
 geom_errorbar(aes(x= 1:8,ymin= avgflux - stddev, ymax= avgflux + stddev), width=0.2, size=1, color= "orange") +
  geom_point(aes(x= 1:8, y= avgflux, color = "orange", size = 3)) + labs( x= "Collar" , y= "Average Flux") + scale_x_continuous(breaks=1:8, labels=c("col1", "col2", "col3", "col4", "col5", "col6", "col7","col8"))
alltrans

```

Collar fluxes by date 

```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}


c1 <- data.frame(col1.1avg, col1.2avg, col1.3avg, col1.4avg, col1.5avg, col1.6avg, col1.7avg)
c2 <- data.frame(col2.1avg, col2.2avg, col2.3avg, col2.4avg, col2.5avg, col2.6avg, col2.7avg)
c3 <- data.frame(col3.1avg, col3.2avg, col3.3avg, col3.4avg, col3.5avg, col3.6avg, col3.7avg)
c4 <- data.frame(col4.1avg, col4.2avg, col4.3avg, col4.4avg, col4.5avg, col4.6avg, col4.7avg)
c5 <- data.frame(col5.1avg, col5.2avg, col5.3avg, col5.4avg, col5.5avg, col5.6avg, col5.7avg)
c6 <- data.frame(col6.1avg, col6.2avg, col6.3avg, col6.4avg, col6.5avg, col6.6avg, col6.7avg)
c7 <- data.frame(col7.1avg, col7.2avg, col7.3avg, col7.4avg, col7.5avg, col7.6avg, col7.7avg)
c8 <- data.frame(col8.2avg, col8.3avg, col8.4avg, col8.5avg, col8.6avg, col8.7avg)
c1 <- t(c1)
c2 <- t(c2)
c3 <- t(c3)
c4 <- t(c4)
c5 <- t(c5)
c6 <- t(c6)
c7 <- t(c7)
c8 <- t(c8)
z <- c("Jul16", "Jul22", "Jul29", "Aug1", "Aug5", "Aug8", "Aug13")
z1 <- c("Jul22", "Jul29", "Aug1", "Aug5", "Aug8", "Aug13")
z1 <- data.frame(z1)
z <- data.frame(z)

c1 <- cbind(c1, z)
c2 <- cbind(c2, z)
c3 <- cbind(c3, z)
c4 <- cbind(c4, z)
c5 <- cbind(c5, z)
c6 <- cbind(c6, z)
c7 <- cbind(c7, z)
c8 <- cbind(c8, z1)

c1$z <- factor(c1$z, levels = c1$z)
c2$z <- factor(c2$z, levels = c2$z)
c3$z <- factor(c3$z, levels = c3$z)
c4$z <- factor(c4$z, levels = c4$z)
c5$z <- factor(c5$z, levels = c5$z)
c6$z <- factor(c6$z, levels = c6$z)
c7$z <- factor(c7$z, levels = c7$z)
c8$z1 <- factor(c8$z1, levels = c8$z1)
cplot <- ggplot() +
geom_point(data = c1, aes(x= z, y=c1), color = "red", size=3) + geom_point(data = c2, aes(x= z, y=c2), color = "orange", size=3)+ geom_point(data = c3, aes(x= z, y=c3), color = "yellow", size=3) + geom_point(data = c4, aes(x= z, y=c4), color = "green", size=3)+ geom_point(data = c5, aes(x= z, y=c5), color = "blue", size=3)+ geom_point(data = c6, aes(x= z, y=c6), color = "purple") +  geom_point(data = c7, aes(x= z, y=c7), color = "black", size=3)+ geom_point(data = c8, aes(x= z1, y=c8), color = "brown", size=3) + labs(x = "Date", y = "Average FLux of collar")
cplot
```

Transect near stream- Blues- lightest blue = col1 (least water) to col4 darkest blue (most water)
Transect near spring- Darkest Green col5 (most water), lightest green col8 (least water)


```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
cplot <- ggplot() +
  geom_line(data = c1, aes(x= z, y=c1, group = 1), color = "lightskyblue", size =2 ) + geom_line(data = c2, aes(x= z, y=c2, group = 1), color = "steelblue1", size =2 )+ geom_line(data = c3, aes(x= z, y=c3, group = 1), color = "dodgerblue3", size =2 ) + geom_line(data = c4, aes(x= z, y=c4, group = 1), color = "blue", size =2 )+ geom_line(data = c5, aes(x= z, y=c5, group = 1), color = "darkgreen", size =2 )+ geom_line(data = c6, aes(x= z, y=c6, group = 1), color = "olivedrab4", size =2 ) +  geom_line(data = c7, aes(x= z, y=c7, group = 1), color = "olivedrab3", size =2 )+ geom_line(data = c8, aes(x= z1, y=c8, group = 1), color = "darkolivegreen1", size =2 ) + labs(x = "Date", y = "Average FLux of collar")
cplot
cplot <- ggplot() +
  geom_line(data = c1, aes(x= z, y=c1, group = 1), color = "brown", size =2 ) +   geom_line(data = c4, aes(x= z, y=c4, group = 1), color = "dodgerblue3", size =2 )+ geom_line(data = c5, aes(x= z, y=c5, group = 1), color = "blue", size =2 )+  geom_line(data = c8, aes(x= z1, y=c8, group = 1), color = "brown", size =2 ) + labs(x = "Date", y = "Average FLux of collar")
#cplot
```
eos2 beside eos1 in water
```{r, eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}

eos2 <- read.csv(here("FieldData/EosFD/eos2_08142019.csv"))
eos2$Year <- paste0("20",eos2$Year)
eos2$dateTime <- as.POSIXct(as.character(paste0(eos2$Year,"-",eos2$Month,"-",eos2$Day," ",eos2$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos2 <- eos2%>%
  select(dateTime,Flux)
colnames(eos2) <- c("DateTime","Flux_eos2")
eos2$Flux_eos2 <- as.numeric(as.character(eos2$Flux_eos2))


eos1 <- read.csv(here("FieldData/EosFD/eos1_08132019.1.csv"))
eos1$Year <- paste0("20",eos1$Year)
eos1$dateTime <- as.POSIXct(as.character(paste0(eos1$Year,"-",eos1$Month,"-",eos1$Day," ",eos1$Time)), format = "%Y-%m-%d %H:%M:%OS")
eos1 <- eos1%>%
  select(dateTime,Flux,Temperature..C.,CO2.Soil..ppm.,
         CO2.Soil.STD..ppm.,CO2.ATM..ppm.,CO2.ATM.STD..ppm.,Mode)
colnames(eos1) <- c("DateTime","Flux_eos1","Temp_C_eos1","CO2_Soil_ppm_eos1","CO2_Soil_STD_ppm_eos1","CO2_ATM_ppm_eos1","CO2_ATM_STD_ppm_eos1","Mode")
eos1$Flux_eos1 <- as.numeric(as.character(eos1$Flux_eos1))

land <- eos2[3078:3251,]
land <- subset(land, format(DateTime,'%OS')=='00')
land <- subset(land, format(DateTime,'%M')%in% c("00","05","10","15","20","25","30","35","40","45","50","55","60"))
row.names(land) <- NULL

water <- eos1[580:753,]
water <- subset(water, format(DateTime,'%OS')=='00')
water <- subset(water, format(DateTime,'%M')%in% c("00","05","10","15","20","25","30","35","40","45","50","55","60"))
row.names(water) <- NULL


landwater <- ggplot() + geom_point(data = land, aes(x= DateTime, y= Flux_eos2), color = "green", size = 1) +
  geom_point(data = water, aes(x=DateTime, y= Flux_eos1), color = "blue", size = 1) + labs(x = "Date", y = "Average FLux")
landwater


landwater <- ggplot() + geom_line(data = land, aes(x= DateTime, y= Flux_eos2), color = "green", size = 1) +
  geom_line(data = water, aes(x=DateTime, y= Flux_eos1), color = "blue", size = 1) + labs(x = "Date", y = "Average FLux")

landwater
```

Blue is Flux from floatation and red is flux from collar 1 from 15:00 on Aug12 to 10:00 Aug13th

```{r , eval=TRUE, warning=FALSE, echo=FALSE, fig.width = 12}
col1night <- eos2[3618:3694,]
row.names(col1night) <- NULL
eos1night <- eos1[1261:1337,]
row.names(eos1night) <- NULL


nightplot<- ggplot() + geom_line(data = col1night, aes(x= DateTime, y= Flux_eos2), color = "red", size = 1) +
  geom_line(data = eos1night, aes(x=DateTime, y= Flux_eos1), color = "blue", size = 1) + labs(x = "Date", y = "Average FLux")
nightplot

```
